Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-17 paper/paper.tex
update Equations 13 and 14

Let us recall the full definition of joint time--frequency scattering:
\begin{equation}
\mathbf{S_2^{\mathrm{joint}}}\boldsymbol{x}(t,\lambda,\alpha,\beta) = 
\left(
\Big\vert
\big\vert
\boldsymbol{x} \overset{t}{\ast} \boldsymbol{\psi}_{\lambda}
\big\vert
\overset{t}{\ast}
\boldsymbol{\psi}_{\alpha}
\overset{\log_2 \lambda}{\ast}
\boldsymbol{\psi}_{\beta}
\Big\vert
\overset{t}{\ast} \boldsymbol{\phi}_{T}
\overset{\log \lambda}{\ast} \boldsymbol{\phi}_{F}\right)(t),
\label{eq:joint-scattering}
\end{equation}
where the symbol $\boldsymbol{\psi}_{\lambda}$ (resp. $\boldsymbol{\phi}_T$) denotes a Morlet wavelet of center frequency $\lambda$ (resp. a Gaussian low-pass filter of scale $T$).
Besides the \emph{joint} time--frequency scattering transform, the generative grammar of scattering transforms \cite{lostanlen2019chapter} also encompasses the \emph{separable} time--frequency scattering transform:
\begin{equation}
\mathbf{S_2^{\mathrm{sep}}}\boldsymbol{x}(t,\lambda,\alpha,\beta) = 
\left(
\bigg\vert
\Big\vert
\big\vert
\boldsymbol{x} \overset{t}{\ast} \boldsymbol{\psi}_{\lambda}
\big\vert
\overset{t}{\ast}
\boldsymbol{\psi}_{\alpha}
\Big\vert
\overset{t}{\ast} \boldsymbol{\phi}_{T}
\overset{\log_2 \lambda}{\ast}
\boldsymbol{\psi}_{\beta}
\bigg\vert
\overset{\log \lambda}{\ast} \boldsymbol{\phi}_{F}
\right)(t),
\label{eq:separable-scattering}
\end{equation}
which has been applied successfully to classify environmental sounds \cite{bauge2013icassp} as well as playing techniques involving periodic modulations \cite{wang2019ismir}.

>>>>

Let us recall the full definition of joint time--frequency scattering (see \lnameref{sec:methods} section):
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\lambda,\alpha,\beta) = 
\left(
\Big\vert
\big\vert
\boldsymbol{x} \overset{t}{\ast} \boldsymbol{\psi}_{\lambda}
\big\vert
\circledast
\boldsymbol{\Psi}_{\alpha,\beta}
\Big\vert
\circledast
\big(\boldsymbol{\phi}_{T} \otimes \boldsymbol{\phi}_{F})
\right)(t,\lambda),
\label{eq:joint-scattering}
\end{equation}
where the $\boldsymbol{\psi}_{\lambda}$ denotes a Morlet wavelet of center frequency $\lambda$ and resp. $\boldsymbol{\phi}_T$ denotes a Gaussian low-pass filter of width $T$.
Besides the \emph{joint} time--frequency scattering transform, the generative grammar of scattering transforms \cite{lostanlen2019chapter} also encompasses the \emph{separable} time--frequency scattering transform:
\begin{equation}
\mathbf{S_2^{\mathrm{sep}}}\boldsymbol{x}(t,\lambda,\alpha,\beta) = 
\left(
\bigg\vert
\Big\vert
\big\vert
\boldsymbol{x} \overset{t}{\ast} \boldsymbol{\psi}_{\lambda}
\big\vert
\ast
\boldsymbol{\psi}_{\alpha}
\Big\vert
\circledast
\big(\boldsymbol{\phi}_{T} \otimes \boldsymbol{\psi}_{\beta}\big)
\bigg\vert
\circledast
\big(\boldsymbol{\phi}_{T} \otimes \boldsymbol{\phi}_F\big)
\right)(t, \lambda),
\label{eq:separable-scattering}
\end{equation}
which has been applied successfully to classify environmental sounds \cite{bauge2013icassp} as well as playing techniques involving periodic modulations \cite{wang2019ismir}.
